Placeholder

### 2021-02-06 Paper_Histograms.Rmd
Added positive OCDs by sample chunk
Added positive psychotic disorders by sample chunk

>>>>

```{r Get OCDs positive by sample}

dat.retro_OCD_by_sample <- dat.retro %>%
  group_by(Sample_plot) %>% 
  select(obsessive_compulsive_disorders_numeric) %>% 
  filter(obsessive_compulsive_disorders_numeric == 1)

dat.retro_OCD_by_sample <- dat.retro_OCD_by_sample %>% 
  group_by(Sample_plot) %>% 
  summarise("OCDs" = n())

```{r Get psychotic disorder positive by sample}

dat.retro_psychosis_by_sample <- dat.retro %>%
  group_by(Sample_plot) %>% 
  select(psychotic_disorders_numeric) %>% 
  filter(psychotic_disorders_numeric == 1)

dat.retro_psychosis_by_sample <- dat.retro_psychosis_by_sample %>% 
  group_by(Sample_plot) %>% 
  summarise("Psychotic disorders" = n())
